Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-15 paper/paper.tex
Removed warnings from Latex source
Additions to the appendix.

Now we use the defintions of $orth_{\vec{u}} \vec{v}$ and $proj_{\vec{u}} \vec{v}$ to simplify equation (\ref{xproperty}).
\begin{align*}
proj_{\vec{u}} \vec{v} = \vec{u} {\vec{u}\cdot\vec{v}\over \vec{u}\cdot\vec{u}}\\
orth_{\vec{u}} \vec{v} = \vec{v} - proj_{\vec{u}} \vec{v}
\end{align*}
Start by squaring both sides of \ref{xproperty} and substituting. Let $\vec{d} = \vec{c}-\vec{l}$, $y = \vec{x}-\vec{l}$.
\begin{align*}
\|\vec{y} - \vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}\|^2 = \|\vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}\|^2 \cdot k^2\\
\vec{y}\cdot\vec{y}-2\vec{y}\cdot\vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}+\vec{d}\cdot\vec{d}({\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}})^2 = (\vec{d}\cdot\vec{d}) ({\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}})^2 \cdot k^2
\end{align*}
Multiply each side by $\vec{d}\cdot\vec{d}$:
\begin{align*}
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-2(\vec{d}\cdot\vec{y})^2+(\vec{d}\cdot\vec{y})^2  = (\vec{d}\cdot\vec{y})^2 \cdot k^2\\
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-(\vec{d}\cdot\vec{y})^2  = (\vec{d}\cdot\vec{y})^2 \cdot k^2
\end{align*}
Now we find the intersection of this cone with the $z=0$ plane.

>>>>

Now we use the defintions of $orth_{\vec{u}} \vec{v}$ and $proj_{\vec{u}} \vec{v}$ to simplify equation (\ref{xproperty}).
\begin{align*}
proj_{\vec{u}} \vec{v} = \vec{u} {\vec{u}\cdot\vec{v}\over \vec{u}\cdot\vec{u}}\\
orth_{\vec{u}} \vec{v} = \vec{v} - proj_{\vec{u}} \vec{v}
\end{align*}
Start by squaring both sides of \ref{xproperty} and substituting. Let $\vec{d} = \vec{c}-\vec{l}$, $y = \vec{x}-\vec{l}$.
\begin{align*}
\|\vec{y} - \vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}\|^2 = \|\vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}\|^2 \cdot k^2\\
\vec{y}\cdot\vec{y}-2\vec{y}\cdot\vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}+\vec{d}\cdot\vec{d}({\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}})^2 = (\vec{d}\cdot\vec{d}) ({\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}})^2 \cdot k^2
\end{align*}
Multiply each side by $\vec{d}\cdot\vec{d}$:
\begin{align*}
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-2(\vec{d}\cdot\vec{y})^2+(\vec{d}\cdot\vec{y})^2  = (\vec{d}\cdot\vec{y})^2 \cdot k^2\\
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-(\vec{d}\cdot\vec{y})^2  = (\vec{d}\cdot\vec{y})^2 \cdot k^2
\end{align*}
Divide both sides by $k^2$ and substitute $k^2 = r^2 / ( L^2-r^2)$.
\begin{align*}
((\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-(\vec{d}\cdot\vec{y})^2)\cdot ( L^2-r^2)/r^2 =  (\vec{d}\cdot\vec{y})^2\\
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})( L^2-r^2)/r^2 =  (\vec{d}\cdot\vec{y})^2(1 + ( L^2-r^2)/r^2)\\
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})( L^2-r^2)/r^2 =  (\vec{d}\cdot\vec{y})^2 L^2/r^2
\end{align*}
The quantities $\vec{d}\cdot\vec{d}$ and $L^2$ are equal (see figure \ref{fig:shadow_1}).
\[
(\vec{y}\cdot\vec{y})( L^2-r^2) =  (\vec{d}\cdot\vec{y})^2
\]
Now we find the intersection of this cone with the $z=0$ plane. The condition for intersection is that the third component of $\vec{x}$ be $0$.
